|

### 2025-01-24 output/seminar-slideshow.qmd
Improve example of "inverse items" in literature
Add item plot

> the negative relation of Item 15 with geometry achievement is particularly puzzling

@@

---@ackerman_multidimensional_2005-1 [p. 17]
:::

@@

>>>>

:::::: columns
:::: {.column width="62%"}
> \[...\] the negative relation of Item 15 with geometry achievement is particularly puzzling.

@@

---@ackerman_multidimensional_2005-1 [p. 17]
:::
::::

::: {.column width="38%"}
![Ítems de "ACT Mathematics Usage Test"](../www/Fig_1-6_Contemporary_Psychometrics.png){fig-align="left"}
:::
::::::

@@

::: aside
Figura tomada de @ackerman_multidimensional_2005-1
:::
